Implementation of Set theory in \dedukti

### 2021-11-15 theoriezf/Article.tex
Update Article.tex

@@

\subsection{Theorems about valuation}

@@

The first term of the conjonction is proved by simple recurrence over natural numbers. The second term of the conjonction is proved by double recurrence. \\

@@

@@

@@

>>>>

We define the symbol $update1$ of type $(\El \ nat \ \ra \ Graph) \ \ra \ \El \ nat \ \ra \ Graph \ \ra \ \El \ nat \ \ra \ (\El \ nat \ \ra \ Graph)$ which obeys the following rewriting rules :

$$update \ \sigma \ x \ a \ y \ \lra \ update1 \ \sigma \ x \ a \ y \ y$$
$$update \ \sigma \ zero \ a \ zero \ z \ \lra \ a$$
$$update \ \sigma \ zero \ a \ (s \ y) \ z \ \lra \ \sigma \ z$$
$$update \ \sigma \ (s \ x) \ a \ zero \ z \ \lra \ \sigma \ z$$
$$update \ \sigma \ (s \ x) \ a \ (s \ y) \ z \ \lra \ update1 \ \sigma \ x \ a \ y \ z$$

@@

\subsection{Results concerning valuation}

@@

\begin{proof}
The first term of the conjonction is proved by simple recurrence over natural numbers. The second term of the conjonction is proved by double recurrence.
\end{proof}

@@

The fourth theorem states that if two valuations are equal they keep being equal after an update.

@@

\begin{proof}
The fifth theorem is proved by induction over formulas.
\end{proof}

@@

\begin{center}
\begin{tabular}{|c|c||c|c|}
\hline Lemma & Number of lines in the proof & Lemma & Number of lines in the proof \\
\hline 3 & ? & 29 & ? \\
\hline 4 & ? & 30 & ? \\
\hline 5 & ? & 31 & ? \\
\hline 6 & ? & 32 & ? \\
\hline 7 & ? & 33 & ? \\
\hline 8 & ? & 34 & ? \\
\hline 9 & ? & 35 & ? \\
\hline 10 & ? & 36 & ? \\
\hline 11 & ? & 37 & ? \\
\hline 12 & ? & 38 & ? \\
\hline 13 & ? & 39 & ? \\
\hline 14 & ? & 40 & ? \\
\hline 15 & ? & 41 & ? \\
\hline 16 & ? & 42 & ? \\
\hline 17 & ? & 43 & ? \\
\hline 18 & ? & 44 & ? \\
\hline 19 & ? & 45 & ? \\
\hline 20 & ? & 46 & ? \\
\hline 21 & ? & 47 & ? \\
\hline 22 & ? & 48 & ? \\
\hline 23 & ? & 49 & ? \\
\hline 24 & ? & 50 & ? \\
\hline 25 & ? & 51 & ? \\
\hline 26 & ? & 52 & ? \\
\hline 27 & ? & 53 & ? \\
\hline 28 & ? & & \\
\hline
\end{tabular}
\end{center}
